5'CutSiteAnalysisDataGeneration

### 2023-08-03 R/CutSiteCorrelationFigureGeneration.rmd
Basic updates to cut site correlation plotting
- Now utilizing shuffling function in associated R script.
- Added figure generation for NHF1 8h timepoint.

  if (shuffle) {
    pairedCutSiteDistances[,Three_Prime_Cut_Site_Distance :=
                             sample(Three_Prime_Cut_Site_Distance, nrow(pairedCutSiteDistances))]
    pairedCutSiteDistances[,Read_Length := Three_Prime_Cut_Site_Distance + Five_Prime_Cut_Site_Distance]
    additionalInformation = paste(additionalInformation,"5'_shuffled")
  }

@@

```{r NHF1_cut_site_correlation_figures}
cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
                                           includedMismatches = "CC>TT")
cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
                                           includedMismatches = "C>T")
cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
                                           omittedMismatches = "C>T")

@@

>>>>

  if (shuffle) {
    pairedCutSiteDistances = getShufflePairedCutSiteDistances(pairedCutSiteDistances)
    additionalInformation = paste(additionalInformation,"5'_shuffled")
  }

@@

```{r NHF1_1h_cut_site_correlation_figures}
cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
                                           includedMismatches = "CC>TT")
cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
                                           includedMismatches = "C>T")
cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "1h", "NHF1", NHF1CutSiteCorrelationDirectory,
                                           omittedMismatches = "C>T")

@@

```{r NHF1_8h_cut_site_correlation_figures}
cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "8h", "NHF1", NHF1CutSiteCorrelationDirectory,
                                           includedMismatches = "CC>TT")
cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "8h", "NHF1", NHF1CutSiteCorrelationDirectory,
                                           includedMismatches = "C>T")
cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "8h", "NHF1", NHF1CutSiteCorrelationDirectory,
                                           omittedMismatches = "C>T")

cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "8h", "NHF1", NHF1CutSiteCorrelationDirectory,
                                           includedMismatches = "CC>TT", shuffle = TRUE)
cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "8h", "NHF1", NHF1CutSiteCorrelationDirectory,
                                           includedMismatches = "C>T", shuffle = TRUE)
cutSiteCorrelationAnalysisFigureGeneration("CPD", "all_reps", "8h", "NHF1", NHF1CutSiteCorrelationDirectory,
                                           omittedMismatches = "C>T", shuffle = TRUE)
```
